---
title: "Hippocampus project"
output:
  html_document: 
    toc: true
    toc_depth: 2 
    toc_float: true
---
# Introduction {#introduction}
Hello, World! This is an intro to the hippocampus project 

## Starting with R studio
debut du projet

## Starting with Github
le mettre en ligne pour collaboration

you can add **bold text asterisc** with aste or two underscores __bold underscore__
you can do *italics single asteri* ou _italics single undescore_
Adding superscript ^withchapeauchinois^
adding subscripts using the ~tilde~
higlight that what you a writing is `code inline code using backtick`  

Use strikethrough text ~~double~~ 

if you're writing a lot of text 
you might want to break it up. one enter ne marche pas 

if you add two enters

it will break up your sentence woop

I want to link my text to the [Introduction section](#introduction)

You can create a [link for Google](https://google.com)

je reference le footnote 1 [^1].

add footnotes comme ca text that appears

[^1]: first footnote, you can put txt or lnks to reference. 

## Lists

ordered list take numbers, mettre un espace ici entre texte et liste:

1. a 
2. b
3. c, I have two items, create sublist using 4 spaces
    a. sub 1
    b. sub 2

* Item C aste creates bullet point
* Item D 

tasks that have been completed or not (creates on github a tickbox or not)
- [ ]
- [x]

you can also link images ![caption of my image a duck](https://images.unsplash.com/photo-1459682687441-7761439a709d?ixlib=rb-1.2.1&ixid=eyJhcHBfaWQiOjEyMDd9&auto=format&fit=crop&w=1410&q=80)

## Tables 

 you can create tables using the upright dash | -

| column header | another colums | 
| ------------- | -------------- |
| first row     | second row     |

> greater than sign to create blocks

used as reminder or block to make something stand out for the reader

how would we highlight code? 

inline code with `single backticks`
if there is a lot of code to highlight three backticks
```
print ("hello, world!")
```
sees code but doesn't run it, to do so R chunk , crtl alt I

```{r}
print("hello, this is the hippocampus project")
75 * 8
```
```{r}
calcul <- 100/2
print(calcul)
```


```{r}
download.file(url="https://raw.githubusercontent.com/cambiotraining/reproducibility-training/master/data/gapminder_data.csv", destfile="data/gapminder_data.csv")
```


chunks you can give them meaningful names when you are on a chunk you can see the list (close to console), message= false chunk option
